A self-consistency check for unitary propagation of Hawking quanta

### 2017-03-06 Draft_BH_shells.tex

In other words, we have proven the following statement:
{\it If we do not see an interference pattern because the quantum uncertainty of the double-slit position is too large and it makes the pattern blurry, then the evolution for the particle alone is not unitarity, because it becomes entangled with the double-slit.}

One might object that the Eq.~(\ref{eq-stdcls}) is not entirely classical, since the value of $\Delta y^{\rm ds}$ has to originate from the unknown quantum mechanics of the double-slit.
Thus, within a classical theory, even if we do not see an interference pattern, we can never know whether $\Delta y^{\rm ds}$ is the true reason that erases the interference pattern.
This is a valid concern, and it actually shows another strength of Eq.~(\ref{eq-stdcls}). 
Indeed we do not know the value of $\Delta y^{\rm ds}$ just from classical physics, but it is very reasonable to assume that it is intrinsic to the double-slit and has a finite value.
Namely, its value should be fixed if we move the screen.
Therefore, there will be a distance too close, such that Eq.~(\ref{eq-stdcls}) is not satisfied, and unitarity of the particle is lost.
There will also be a distance far enough, such that Eq.~(\ref{eq-stdcls}) is satisfied, and the subsystem unitarity for the particle is valid.
At the level of gedanken experiment, we would always want to make sure that the second case is true.

@@

The double-slit experiment is an example where both the classical coherence and quantum unitarity can be calculated explicitly and shown to follow the same condition.
Here, we advocate that such a relation is actually a general rule.
{\it Classical coherence, instead of thinking of it as a practicality of measurements, should be treated as a prerequisit to quantum unitarity.} 
Thus when classical coherence fails, not only have we no practical measurements to confirm the purity of the subsystem wavefunction, such wavefunctions {\it actually did not evolve unitarily.}
Whatever effect responsible for a classical uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem quantum-mechanically and became entangled with it.

>>>>

In other words, we have proven the following statement:
The quantum uncertainty of the double-slit position is too large and makes the interference pattern blurry {\bf if and only if} the evolution for the particle alone is not unitarity due to entanglement with the double-slit.

One might object that the Eq.~(\ref{eq-stdcls}) is not entirely classical, since the value of $\Delta y^{\rm ds}$ has to originate from the unknown quantum mechanics of the double-slit.
Thus, within a classical theory, even if we do not see an interference pattern, we can never know whether the quantum uncertainty, $\Delta y^{\rm ds}$, is the true reason that erases the interference pattern.
This is a valid concern, and it actually shows another strength of Eq.~(\ref{eq-stdcls}). 
Indeed we do not know the value of $\Delta y^{\rm ds}$ just from classical physics, but it is very reasonable to assume that it is intrinsic to the double-slit and has a finite value.
Namely, its value should be fixed if we move the screen.
Therefore, there will be a distance too close, such that Eq.~(\ref{eq-stdcls}) is not satisfied, and unitarity of the particle is lost.
There will also be a distance far enough, such that Eq.~(\ref{eq-stdcls}) is satisfied, and the subsystem unitarity for the particle is valid.
At the level of gedanken experiment, we would always want to make sure that the second case is true.

@@

The double-slit experiment is an example where both the classical coherence and quantum unitarity can be calculated explicitly and shown to follow the same condition.
Here, we advocate that such a relation is actually a general rule.
{\it Classical coherence, instead of thinking of it as a practicality of measurements, should be treated as a prerequisit to quantum unitarity.} 
Thus when classical coherence fails, not only have we no practical measurements to confirm the purity of the subsystem wavefunction, such wavefunctions {\it actually did not evolve unitarily.}
Whatever effect responsible for a quantum uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem and became entangled with it.
